|

### 2020-01-31 paper/cogsci/paper_jan28.Rmd
Incorporating GK's edits

Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam]. In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.

With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.  Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that many frames are typically not inspected, even in the most comprehensive studies. For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage. To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1). In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces [MTCNN, @zhang2016].

@@

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained human annotations for a subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` % of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure \ref{fig:handLocation}.

@@

```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant."}
cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
```

@@

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filme and scaled by the number of frames in that age range. Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands. Bins with less"}

@@

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on the entire dataset. This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may still be an underestimate of the proportion of hands in view. Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects, but also the children’s own hands, leading to more frequent hand detections.

@@

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view. This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100` %. Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands(see Figure \ref{fig:handLocation}).  Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).

@@

How does variability across different contexts influence the social information in the infant view? 
Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in. `r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames (see @SAYcam). Activities varied somewhat predictability by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children.  For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchen (see Figure \ref{fig:DetByLocation}).

@@

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos. Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly--leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children. Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations. This variability likely stems from the fact that thereare at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to face and hands. While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

>>>>

Here, we examine the social information present in the infant visual perspective--the presence of faces and hands--by analyzing a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYcam dataset [@SAYcam]. In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted cameras used in the SAYcam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail to capture short saccades to either faces or hands in the periphery, as the timescale of head movements is much longer.

With hundreds of hours of footage (>40M frames), however, this large dataset necessitates a shift to an automated annotation strategy.  Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage. To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1). In prior work with egocentric videos, [@sanchez2018postural]  OpenPose performed comparably to other detectors specified for detecting only faces [MTCNN, @zhang2016].

@@

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose—-a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via AMT) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100` % of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Figure \ref{fig:handLocation}.

@@

```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=2, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant. Brighter values indicate more detections."}
cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
```

@@

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3.5, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show the proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands. Bins with less"}

@@

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset) or OpenPose annotations on the entire dataset. This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may still be an underestimate of the proportion of hands in view. Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYcam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

@@

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view. This decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%. Note that this cropping likely removes both the majority of detections of children's own hands but does also remove some detections of adult hands (see Figure \ref{fig:handLocation}), as especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see Figure \ref{fig:FacesAndHands}).

@@

How does variability across different contexts influence the social information in the infant view? 
Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location that the videos were filmed in. `r videos_included` were filmed in single location, representing 17 percent of the dataset and over 5 million frames [@SAYcam]. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children.  For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchen (see Figure \ref{fig:DetByLocation}).

@@

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field of view to the upper 60% of the visual field of the videos to make the analyses more comparable to previous work [@Fausey2016]. Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly--leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activites, showing differences across locations and between individual children. Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S  more faces in the kitchen than in other locations. This variability likely stems from the fact that thereare at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to face and hands. While the social information in view may be variable across children in different activitiy contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
